---
title: "OxShef: Tools"
output:
  html_document:
    toc: false
    toc_float:
      collapsed: false
    includes:
      before_body: [includes/include_header.html, includes/include_header_navpage.html]
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```


<link href="https://use.fontawesome.com/releases/v5.0.6/css/all.css" rel="stylesheet">

## Visualisation Tools

There are hundreds of visualisation tools and packages used by researchers for communicating research datasets. **OxShef: Tools** cannot hope to be a reference or a recommendation engine for all of these solutions. We maintain a collection of the most popular/versatile tools [below](#table-of-tools). For a birds eye view of the entire range of dataviz tools avaialble, you might find this resource useful: http://www.visualisingdata.com/resources/.


<p>
  <a class="btn btn-primary" data-toggle="collapse" href="#table-description" role="button" aria-expanded="false" aria-controls="collapseExample">
    Learn more about this table...
  </a>
</p>
<div class="collapse" id="table-description">
  <div class="card card-body">

<br>

<div class='row'>

<div class='col-sm-6'>

<center><h5>Data **can be** pulled from external sources  <i class='fas fa-circle'></i></i></h5></center>
Tools that can pull data from external sources fullfil **OxShef: Tools** [reproducible dataviz workflow requirements](reproducible-dataviz-workflow.html) and are highly recommended by us. In general, we will provide a dedicated website for such tools in [the table below](#table-of-tools).

</div>

<div class='col-sm-6'>

<center><h5>Data **cannot** pulled from external sources  <i class='far fa-circle'></i></i></h5></center>
As data cannot be pulled directly from a data repository, these tools **do not** meet **OxShef: Tools** [reproducible dataviz workflow requirements](reproducible-dataviz-workflow.html). You will be required to duplicate your data on the visualisation service's website, which makes keeping your visualisation consistent with your canonical datset difficult.

</div>

</div>

Visualisation tools fit neatly into these two categories, either of these may be suitable for a [reproducible dataviz workflow](reproducible-dataviz-workflow.html).

<div class='row'>

<div class='col-sm-6'>

<center><h5>Point and Click Tools <i class='fa fa-hand-pointer'></i></h5></center>
These allow users to build visualisations interactively, for instance selecting columns from a spreadsheet-like view of your data and clicking "Create BarChart". Examples of this type of tool include: **Excel**, **SPSS** and **Tableau**.

</div>

<div class='col-sm-6'>

<center><h5>Scripting Tools <i class='fa fa-file-code'></i></h5></center>
These require users to write code (or scripts) to generate visualisations, such tools in general have a steeper initial learning curve than "point and click tools" but allow greater overall flexibility  and extensibility. Examples of this type of tool include: **Python**, **R**.
</div>
</div>

<br/>
</div>
</div>





<a name='table-of-tools'></a>

```{r viz-tools-DT, echo = FALSE}
library("tidyverse")
library("DT")
library("readxl")

fa_scripting <- "<i class='fa fa-file-code fa-2x'></i>"
fa_pointAndClick <- "<i class='fa fa-hand-pointer fa-2x'></i>"

fa_icons <- tribble(
  ~tool.type, ~type,
  "Scripting", "<i class='fa fa-file-code fa-2x'></i>",
  "Point and Click", "<i class='fa fa-hand-pointer fa-2x'></i>"
)

oxshef_viz_tools <- read_xlsx("oxshef-viz-tools.xlsx")

oxshef_viz_tools %>%
  arrange(tool) %>%
  mutate(logo = paste0(
    "<a href='", url, "' target='_blank'>",
    "<img src='images/table-of-tools-logos/", image.path, "' style='max-height:80px'></img>",
    "</a>"
  )) %>%
  left_join(fa_icons) %>%
  select(-url, -tool.type, -image.path, -tool) %>%
  mutate(external.data.support = ifelse(external.data.support,
    "<i class='fas fa-circle'></i>",
    "<i class='far fa-circle'></i>"
  )) %>%
  select(logo, everything()) %>%
  datatable(
    escape = FALSE,
    rownames = FALSE,
    colnames = c(
      "Visualisation Tool",
      "Brief Description",
      "Allows external data to be accessed?",
      "Type of tool"
    ),
    options = list(
      scrollX = TRUE,
      autoWidth = TRUE,
      columnDefs = list(
        list(width = "100px", targets = c(0, 2)),
        list(className = "dt-center", targets = c(0, 2, 3))
      ),
      dom = "t"
    ),
    width = "100%"
  )
```