---
title: "OxShef: Tools"
output:
  html_document:
    toc: false
    toc_float:
      collapsed: false
    includes:
      before_body: [includes/include_header.html, includes/include_header_navpage.html]
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```


<link href="https://use.fontawesome.com/releases/v5.0.6/css/all.css" rel="stylesheet">

# Visualisation Tools

There are hundreds of visualisation tools and packages used by researchers for communicating research datasets. **OxShef: Tools** cannot hope to be a reference or a recommendation engine for all of these solutions. For a birds eye view of what tools are available you might find this resource useful: http://www.visualisingdata.com/resources/.

In general, visualisation tools fall into one of two categories:

- Point and Click Tools <i class='fa fa-hand-pointer'></i>: These allow users to build visualisations interactively, for instance selecting columns from a spreadsheet-like view of your data and clicking "Create BarChart". Examples of this type of tool include: **Excel**, **SPSS** and **Tableau**.
- Scripting Tools <i class='fa fa-file-code'></i>: These require users to write code (or scripts) to generate visualisations, such tools in general have a steeper initial learning curve than "point and click tools" but allow greater overall flexibility  and extensibility. Examples of this type of tool include: **Python**, **R**.

We further sub-divide tools by their ability to pull data from external sources, i.e. from a DOI-issuing data repository.

```{r viz-tools-DT, echo = FALSE}
library("tidyverse")
library("DT")
library("readxl")

fa_scripting <- "<i class='fa fa-file-code fa-2x'></i>"
fa_pointAndClick <- "<i class='fa fa-hand-pointer fa-2x'></i>"

fa_icons <- tribble(
  ~tool.type, ~type,
  "Scripting", "<i class='fa fa-file-code fa-2x'></i>",
  "Point and Click", "<i class='fa fa-hand-pointer fa-2x'></i>"
)

oxshef_viz_tools <- read_xlsx("oxshef-viz-tools.xlsx")

oxshef_viz_tools %>%
  arrange(tool) %>%
  mutate(tool = paste0("<a href='", url,"' target='_blank'>", tool, "</a>")) %>%
  left_join(fa_icons) %>%
  select(-url, -tool.type) %>%
  mutate(external.data.support = ifelse(external.data.support,
                                         "<i class='fas fa-circle'></i>",
                                         "<i class='far fa-circle'></i>")) %>%
  datatable(escape = FALSE,
            rownames = FALSE,
            colnames = c("Visualisation Tool",
                         "Brief Description",
                         "Allows external data to be accessed?",
                         "Type of tool"),
            options = list(
              scrollX = TRUE,
                autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = c(0,2)),
                    list(className = 'dt-center', targets = c(0,2,3))),
              dom = "t"
            ),
  width = "100%")
```